---
title: "Bridge data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

# The reason why I use the fread is because after trying to use read.csv and read_csv, fread won't give any warning
# messages and it just solves many problems if I use the code read.csv and read_csv
```{r cars}
library(data.table)
AK19 = fread("AK19.csv")
```

#validation of the data
#from the officail website, I have already known the number of observations and number of the columns
```{r pressure, echo=FALSE}
str(AK19)
```

#Choose few interesting columns
```{r}
library(dplyr)
select(AK19, STRUCTURE_NUMBER_008,YEAR_BUILT_027, COUNTY_CODE_003,SUBSTRUCTURE_COND_060,SUPERSTRUCTURE_COND_059)
```



